Model LF

### 2022-11-01 prod test.Rmd
commit

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot(((emp_05 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in Employment (people)", main= "Employment");
lines(((emp_03 - emp_bs3)*1000), col= "black");
legend("left", legend=c("All channels","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

>>>>

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot(((unemp_05 - unemp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in Employment (people)", main= "Employment");
lines(((unemp_03 - unemp_bs3)*1000), col= "black");
legend("left", legend=c("All channels","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```
